Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
typo

\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
which may restricts the observability of the state-space from the output space.
\begin{equation}
\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
\end{equation}

>>>>

\noindent with $\vec{w} \sim \mathcal{N}(0,Q)$.\\
Furthermore, a control system may have a derived output that is a linear combination of its states and inputs, 
which may restrict the observability of the state-space from the output space.
\begin{equation}
\vec{y}(t)=\vec{C}\vec{x}(t)+\vec{D}\vec{u}(t).
\end{equation}
